\LARGE \bf Optimal Joint Probabilistic Data Association Filter\\ Avoiding Coalescence in Close Proximity

### 2018-06-09 Conference/ECC 2014/last_bit.tex
added Conference folder

Data association is a heavily studied field with many applications in estimation when measurements are not necessarily originating from a single target.
We consider applications wherein multiple targets of interest enter the field of view of a sensor; however, the measurement origin is unknown.
To properly track these targets, we require estimation techniques to associate targets with measurements.
When the targets are in very close proximity, the association uncertainty grows, and an effective algorithm is necessary to maintain close estimations of the targets.

A variety of data association techniques are considered for the close-proximity data association with varying performance.
Some approaches such as multiple hypothesis tracking (MHT) and probability hypothesis density (PHD) techniques involve a high computational load, especially when targets are in close proximity, making real-time implementation more difficult~\cite{MHT1},~\cite{PHD1}, and~\cite{PHD2}.
Many other techniques may involve the Kalman filter (KF) or extended KF (EKF), which are well studied and provide a framework for recursive data association techniques that are much easier to implement in real-time.
A common heuristic approach is known as the nearest neighbor filter (NNF), which is a simple algorithm that only updates estimates for measurements with the closest square Mahalnobis distance, updating other targets only with their predictions~\cite{NN2}.
This is considered a \emph{hard decision} in~\cite{JPDAF1}, or that every measurement update receives full weighting; if the decision is incorrect, these measurement updates can result in detrimental effects to the associations of the estimates, so this technique is avoided in the analysis of this paper.
Alternatively, some approaches calculate the minimum mean square error (MMSE) of the estimates and their associated uncertainty.
The probabilistic data association (PDA) technique is effective in tracking a single target because it updates with a \emph{soft decision}; in particular, this approach updates provides a weighting from a likelihood of measurement association.

The joint PDA (JPDA) is an extension of the PDA to incorporate multiple targets~\cite{JPDAF1},~\cite{TrackDataAssoc}.
The JPDA filter (JPDAF) is particularly advantageous in multi-target scenarios because when targets share measurements, the soft decisions prevent loss of information, which occurs with hard decisions.
However, when neighboring targets share measurements, the estimates are subject to coalescence.

Most techniques to avoid track coalescence involve pruning the tracks, or designing a set of rules that limit the possible outcomes to likely scenarios. These rules typically involve the exact nearest neighbor probabilistic data association (ENNPDA), which applies a strong decision to the most likely associated estimate. Pruning algorithms incorporate the ENNPDA algorithm because  estimates do not share measurements, making it insensitive to track coalescence~\cite{Coal1}. For example in~\cite{Fitzgerald}, the algorithm involves a set of rules to prune the tracks that share measurements. The algorithm considers the possible tracks and applies a logic that assigns estimates to likely scenarios; a set of possible tracks are considered and lower likelihood track scenarios are deleted. Updates to tracks considered likely are given a strong decision. This technique is extended in~\cite{Coal_d},~\cite{Coal_e}, and~\cite{Coal_c} because of its successful resistance to coalescence. However, track pruning assumes that low likelihood tracks are incorrect, which is not necessarily true. Removing the weighting scheme of the JPDA causes the estimates to lose information, which this paper seeks to avoid.

We propose a novel approach to removing coalescence by minimizing a similarity index of the estimates.
Instead of choosing a different means of weighting the measurement updates, we design an optimal recursive estimation algorithm that chooses gains to compensate for the effects of coalescence.
The algorithm derived in this paper can be applied in real-time without the heuristic nature, loss of information, or the risk of hard decisions from the current coalescence avoidance approaches.

The paper is organized as follows: the problem is formally presented in Section \ref{ProbDef}.
The derivation and explanation of a modified JPDAF under the assumptions of this paper is described in Section \ref{JPDAF}.
The optimal gain that minimizes a weighted cost of uncertainty and similarity is derived in Section \ref{C-JPDAF}.
We consider a satellite tracking example of this technique in Section \ref{NumRes}.
Finally, we discuss results and applications for the C-JPDAF in Section \ref{ConclusionFutureWork}.

% Dr. Lee Edits:
\section{Data Association Filtering Problem Formulation}
\label{ProbDef}

@@

More explicitly, let $\Theta_i$ be the event that the measurement originated from the $i$-th target, for $i\in\{1,2\}$. According to the above assumptions, we have
\begin{align}
P(\Theta_1\cup \Theta_2)&=1,\quad
P(\Theta_1\cap \Theta_2)=0,\\
P(\Theta_1)&=P(\Theta_2)=0.5.\label{eqn:MeaOrig}
\end{align}

@@

A filtering problem is formulated as recursively updating the estimated state of each target and its covariance, namely $(\hat x_{i_k}, P_{i_k})$ based on the above assumptions given by \refeqn{xkp}--\refeqn{MeaOrig}. In particular, we wish to avoid track coalescence when two targets are in close proximity.

@@

\subsection{Flow Update}
Similar to Kalman filters, the JPDAF is composed of a flow update and a measurement update. During the flow update (or prediction step), the estimated state $\hat x_{i_k}$ and its covariance $P_{i_k}$ of each target are updated as in the standard filter as follows:
\begin{gather}
\hat x_{i_{k}} = A_{i_{k-1}} \hat x_{i_{k-1}},\\
P_{i_{k}} = A_{i_{k-1}} P_{i_{k-1}} A_{i_{k-1}}^T + Q_{i_{k-1}}.
\end{gather}
These are initialized by \refeqn{xi0}, and they are repeated between measurements.

@@

The data association probability is defined as follows. Let $\beta_i$ be the probability of the $i$-th data association event conditioned by the given measurement:
\begin{align*}
\beta_{i_k} = P[\Theta_i|z_k].
\end{align*}
For the given assumptions summarized in Section \ref{ProbDef}, it can be obtained as
\begin{align}
\beta_{i_k}=\frac{f_{i_k}}{\sum\limits_{y=1}^2 f_{i_k}},\label{eqn:betaik}
\end{align}
where $f_{i_k}$ is defined as
\begin{align}
f_{i_k}=\mathcal{N}[z_{k};\hat z_{i_{k|k-1}},S_{i_k}].
\end{align}
Here $\mathcal{N}[x;\mu,\Sigma]$ denotes the Gaussian probability density function of mean $\mu$ and covariance matrix $\Sigma$ evaluated at $x$ (see Appendix for the derivation of \refeqn{betaik}).

According to the total probability theorem with respect to the association events, the resulting posterior estimate of the state is given by
\begin{align}
\hat x^+_{i_k}=&\hat x^-_{i_k}+\beta_{i_k}K_{i_k}e_{i_k}\label{KalEst},
\end{align}
where the estimator gain is equal to the Kalman gain, i.e., $K_i = P_{i_k}^{-} H_{i_k}^T S_{i_k}^{-1}$, as there is no measurement origination uncertainty when conditioned on the event $\Theta_i$.

@@

The joint probabilistic data association filter described in the previous section is effective in handling clutter or missed detection of multiple targets. However, it is prone to coalescing estimates, especially with targets in close-proximity. Here, we present a coalescence-avoiding optimal JPDAF, hereafter C-JPDAF for short, to avoid data coalescence. The main idea is choosing the estimator gain such that a weighted sum of the size of uncertainty and a measure of similarity is minimized.

@@

The initial estimate of the states are designed to occur shortly before the two trajectories cross paths near $r_{ref}=7000km$ from the center of the earth; for the time to complete a circular orbit at this radius, $t_{ref}=2\pi \sqrt{\frac{r_{ref}^3}{\mu}}$, we can solve for a reference circular orbit $X_{ref}=\begin{bmatrix} r_{ref} & 0 & 0 & \frac{2\pi}{t_{ref}}\end{bmatrix}^T$, then perturb this orbit slightly by $X_{pert}=\begin{bmatrix} 0.40 & 0 & 0 & -1.5\times10^{-5}\end{bmatrix}^T$. We can easily choose the initial conditions to be $X_{1_0}= X_{ref}+X_{pert}$ and $X_{2_0}= X_{ref}-X_{pert}$. The initial estimates are assumed to be relatively accurate: there is no need to simulate large uncertainty when the paths are initially sufficiently far apart because this paper is concerned with the coalescence when the targets are close together, so the state and covariance will have been determined by simulated measurements while the estimates were still spread significantly apart; hence for both estimates, the initial covariance was chosen to be $P_0=diag(\begin{bmatrix}
2.5\times10^{-4} & 2.5\times10^{-6} & 3.9\times10^{-8} & 3.9\times10^{-8} \end{bmatrix})$.
The process noise was chosen to be equivalent for both estimate such that $Q=diag(\begin{bmatrix}
2.5\times10^{-5} & 2.5\times10^{-7} & 3.9\times10^{-9}& 3.9\times10^{-9}\end{bmatrix})$ and $R=\begin{bmatrix}
2.25\times10^{-2}
\end{bmatrix}$ applied at each time step.

Three filtering approaches are applied, namely extended Kalman filter (EKF), JPDAF, and C-JPDAF, such that a single measurement was evaluated at each time step, and its origination was random and equally likely from both targets. For EKF, it is assumed that the correct measurement origination is know with certainty, i.e., all of the measurements are associated to correct target. This serves as an ideal reference case to be compared with JPDAF and C-JPDAF. For the C-JPDAF, the weighting parameters of the cost are chosen as $a=0.02$ and $c=5\times10^{-5}$. We propagate the nonlinear equations of motion numerically using Matlab, and we generate measurement at every $0.1$ seconds with an equal likelihood that its origination is from either target.

@@

\begin{table}
\caption{Estimation results}\label{tab:RMS}
\centerline{
\begin{tabular}{ccc}\hline
Method & Radial RMS Error (km) & Computation time (sec) \\\hline
EKF & 1.438e-05 &6.118\\
JPDAF & 7.1242e-05 &6.130\\
C-JPDAF & 2.3145e-05  & 19.864 \\\hline
\end{tabular}}
\end{table}

@@

We incorporate all of the assumptions from Section \ref{DAP} to simplify the weighting term for the estimates.
We consider time step $k$ for the following proofs so subscripts omitted in this appendix.
We define ${\bf{\Theta}}\in[\Theta_1, \Theta_2]$, as all possible outcomes, namely that target $1$ is measured or target $2$ is measured from $m_k=1$ total measurements. Because all events ${\bf{\Theta}}$ fall inside an arbitrary volume $V$, or are subject to being measured, we define the measurement association indicator $\tau=1$, meaning that measurement $k$ is associated with exactly one of the two targets. Hence, the number of unassociated measurements $\phi({\bf{\Theta}})=0$ because the event that neither target is measured $\Theta_0\notin{\bf{\Theta}}$. We define the binary target detection indicator $\delta_i(\Theta_i)$, which indicates the association of any measurement with target $i$; hence, $\delta_i(\Theta_i)=1$ if measurement $k$ is associated with target $i$ and $\delta_i(\Theta_i)=0$ otherwise.
We also consider equal likelihood of detection $P(\Theta_i)$ for each measurement; we can generalize the number of estimates to $y$ such that $P(\Theta_i)=\frac{1}{y}$ for equal likelihood of event $\Theta_i$.
From~\cite[Section 9.3]{TrackDataAssoc}, we determine the weighting for $T$ possible targets to be
\begin{align}
\beta_i\equiv P(\Theta_i|z)=&\frac{1}{c}\frac{\phi!}{V}\displaystyle\prod_{j=1}^{m_k} f_{i_j}^{\tau_j}\displaystyle\prod_{i=1}^{T} P(\Theta_i)^{\delta_i}(1-P(\Theta_i))^{1-\delta_i}\\
=&\frac{1}{cV}f_{i}\frac{1}{y}(1-\frac1y)^{T-1}
\end{align}
for normalizing constant $c$ and Gaussian pdf $f_{i}$. Note that $T-1$ targets are not associated and only one target is associated. Hence, $c$ is defined as
\begin{align}
c=&\frac{1}{V}\frac{1}{y}(1-\frac1y)^{T-1}\displaystyle\sum\limits_{l=1}^y f_{l}.
\end{align}
Therefore, we solve for the simplified weighting
\begin{align}
\beta_i=\frac{f_i}{\displaystyle\sum\limits_{l=1}^y f_{l}}
\end{align}
which is much simpler after assumptions.

The second proof shows how the measurement updates may take a more manipulatable form under the assumptions. From~\cite[Section 6.4]{TrackDataAssoc},
\begin{align}
\bar e=&\displaystyle\sum\limits_{i=1}^{m_k}\beta_ie_i=\beta_ie_i\\
\hat x^+_i=&\hat x^-_i+K_i\bar e=\hat x^-_i+\beta_iK_ie_i.
\end{align}
 , so this portion of the covariance Let $\tilde{P}$ be spread in the innovations term on each target. Because only one innovation is calculated per target, there is no spread in this term; hence $\tilde{P}=0$. Note that his term would be nonzero in the JDPAF without the single measurement assumption. Let $P_{i}^C$ be the posterior covariance of target $i$ conditioned on event $\Theta_i$. For any $K_i$ from ~\cite[Section 4.2]{OptEst1}:
\begin{align}
\begin{split}
P_{i}^C=&(I-K_{i}H_{i})P_{i}^{-}(I-K_{i}H_{i})^T+K_{i}R_{i}K_{i}^T\\
=&P^--K_{i}H_{i}P_{i}^{-}-P_{i}^{-}H_{i}^TK_{i}^T\\
&+K_{i}(H_{i}P_{i}^{-}H_{i}^T+R_i)K_{i}^T.
\end{split}
\end{align}
We define $\beta_{0_i}$ as the probability that target $i$ is not measured; with only one measurement considered each time step; hence, $\beta_{0_i}=1-\beta_i$. Again from~\cite[Section 6.4]{TrackDataAssoc},
\begin{align}
\begin{split}
P^+_i=&\beta_{0_i}P^-_i+(1-\beta_{0_i})P_i^C+\tilde{P}\\
=&(1-\beta_i)P^-+\beta_i[P^--K_{i}H_{i}P_{i}^{-}\\
&-P_{i}^{-}H_{i}^TK_{i}^T+K_{i}(H_{i}P_{i}^{-}H_{i}^T+R_i)K_{i}^T]\\
=&P^-_i-\beta_i[K_{i}H_{i}P_{i}^{-}+P_{i}^{-}H_{i}^TK_{i}^T\\
&-K_{i}(H_{i}P_{i}^{-}H_{i}^T+R_i)K_{i}^T].
\end{split}
\end{align}

@@

\bibliography{BibMaster}
\bibliographystyle{IEEEtran}
\end{document}

%Many techniques to avoid track coalescence involve the concept that when the exact nearest neighbor probabilistic data association (ENNPDA) is applied, which associates a measurement with a strong decision to the most likely estimate, the estimates are insensitive to track coalescence~\cite{Coal1}.
%By pruning the tracks, or designing a set of rules to determine high likelihood scenarios, an algorithm choice or weighing scheme is applied to the measurement updates.
%For example in~\cite{Fitzgerald}, the algorithm involves a set of rules based on the data received with respect to the estimates.
%A special logic is introduced that determines how weighting of the updates is defined or if a new track should be considered.
%In some cases, it is possible for an incorrectly associated estimate measurement may receive full weighting in the update.
%Other criteria or extensions of this approach are detailed in~\cite{Coal_d},~\cite{Coal_e}, and~\cite{Coal_c}, which can be very effective, but information may be lost when measurements are omitted from updating an estimates with small probabilities of association because the pruning rule prevented these association possibilities.

>>>>

Data association has been widely studied with various applications in estimation of a single or multiple targets with measurements that are not necessarily originating from correct targets in order. To properly track multiple targets with measurement origin uncertainties, measured data should be properly associated to targets with certain probabilities. %When the targets are in very close proximity, the association uncertainty grows, and an effective algorithm is required to maintain close estimations of the targets. Otherwise, estimators tend to coalesce neighboring tracks.

%This paper considers estimation wherein multiple targets of interest enter the field of view of a sensor; however, the measurement origin is unknown.

A variety of data association techniques with varying performance have been studied. A common heuristic approach is known as the nearest neighbor filter (NNF), where measurements with the closest distance are only applied~\cite{NN2}. This is considered a \emph{hard decision} in~\cite{JPDAF1}, as every selected measurement update receives full weighting. Therefore, if the decision is incorrect, these measurement updates can result in detrimental effects to the associations of the estimates.  Alternatively, there are approaches that calculate the minimum mean square error (MMSE) of the estimates and their associated uncertainty. The probabilistic data association (PDA) technique is effective in tracking a single target because it updates with a \emph{soft decision}; in particular, this approach updates provides a weighting from a likelihood of measurement association. Other approaches include multiple hypothesis tracking (MHT) and probability hypothesis density (PHD) techniques~\cite{MHT1,PHD1,PHD2}.

%Many other techniques may involve the Kalman filter (KF) or extended KF (EKF), which are well studied and provide a framework for recursive data association techniques that are much easier to implement in real-time.

The joint PDA (JPDA) is an extension of the PDA to incorporate multiple targets~\cite{JPDAF1},~\cite{TrackDataAssoc}.
The JPDA filter (JPDAF) is particularly advantageous in multi-target scenarios because when targets share measurements, the soft decisions prevent loss of information that occurs with hard decisions. As such, it is well known that JPDAF are effective in handling data clutter or missed detection. However, when the targets are in very close proximity, the association uncertainty grows significantly, thereby degrading the filtering performance. Furthermore, the estimated probability distributions tend to be coalesced especially if the paths of neighboring targets cross with each other.

%neighboring targets share measurements, the estimates are subject to coalescence.

Many techniques to avoid track coalescence involve the concept that when the exact nearest neighbor probabilistic data association (ENNPDA) is applied, which associates a measurement with a strong decision to the most likely estimate, the estimates are insensitive to track coalescence~\cite{Coal1}. By pruning the tracks, or designing a set of rules to determine high likelihood scenarios, an algorithm choice or weighing scheme is applied to the measurement updates.
For example in~\cite{Fitzgerald}, the algorithm involves a set of rules based on the data received with respect to the estimates. A special logic is introduced that determines how weighting of the updates is defined or if a new track should be considered. In some cases, it is possible for an incorrectly associated estimate measurement may receive full weighting in the update. Other criteria or extensions of this approach are detailed in~\cite{Coal_d},~\cite{Coal_e}, and~\cite{Coal_c}, which can be very effective, but information may be lost when measurements are omitted from updating an estimates with small probabilities of association because the pruning rule prevented these association possibilities.

This paper is focused on optimal joint probabilistic data association filter that avoids coalescence in close proximity. We propose a novel approach to remove coalescence by minimizing a similarity index of the estimates. More explicitly, the gain of the proposed estimator is chosen such that a weighted sum of the size of uncertainties and a similarity measure between estimated states is minimized at each update. This yields an optimal recursive estimation algorithm that compensates for the effects of coalescence systematically. The proposed approach has simpler structures compared with pruning-based approaches, and it is computationally efficient. As it is still based on probabilistic data association, it avoids the heuristic nature, loss of information, or the risk of other coalescence avoidance approaches based on hard-decision.

The paper is organized as follows: the dynamics of target and the measurement models are described in Section \ref{ProbDef}. The proposed Coalescence Avoiding Optimal JPDAF (C-JPDAF) are presented at Sections \ref{JPDAF}, and the optimal gain that minimizes a weighted cost of uncertainty and similarity is derived in Section \ref{C-JPDAF}.
These are illustrated by a numerical example for estimating two satellites in crossing orbits in Section \ref{NumRes}, followed by conclusions in Section \ref{ConclusionFutureWork}.

\section{Data Association Filtering Problem Formulation}
\label{ProbDef}

@@

More explicitly, let $\Theta_i$ be the event that the measurement is originated from the $i$-th target, for $i\in\{1,2\}$. According to the above assumptions, we have
\begin{align}
P(\Theta_1\cup \Theta_2)&=1,\quad
P(\Theta_1\cap \Theta_2)=0,\\
P(\Theta_1)&=P(\Theta_2)=0.5.\label{eqn:MeaOrig}
\end{align}

@@

A filtering problem is formulated as recursively updating the estimated state of each target and its covariance, namely $(\hat x_{i_i}, P_{i_i})$ based on the above assumptions given by \refeqn{xkp}--\refeqn{MeaOrig}. In particular, we wish to avoid track coalescence when two targets are in close proximity.

@@

\subsection{Flow Update}
Similar to Kalman filters, JPDAF is composed of flow update and measurement update. At flow update (or prediction step), the estimated state $\hat x_{i_k}$ and its covariance $P_{i_k}$ of each target are updated as in the standard filter as follows:
\begin{gather}
\hat x_{i_{k}} = A_{i_{k-1}} \hat x_{i_{k-1}},\\
P_{i_{k}} = A_{i_{k-1}} P_{i_{k-1}} A_{i_{k-1}}^T + Q_{i_{k-1}}.
\end{gather}
These are initialized by \refeqn{xi0}, and they are repeated between measurements.

@@

The date association probability is defined as follows. Let $\beta_i$ be the probability of the $i$-th data association event conditioned by the given measurement:
\begin{align*}
\beta_{i_k} = P[\Theta_i|z_k].
\end{align*}
For the given assumptions summarized in Section \ref{ProbDef}, it can be obtained as
\begin{align}
\beta_{i_k}=\frac{f_{i_k}}{\sum\limits_{y=1}^2 f_{i_k}},\label{eqn:betaik}
\end{align}
where $f_{i_k}$ is defined as
\begin{align}
f_{i_k}=\mathcal{N}[z_{k};\hat z_{i_{k|k-1}},S_{i_k}].
\end{align}
Here $\mathcal{N}[x;\mu,\Sigma]$ denotes the Gaussian probability density function of mean $\mu$ and covariance matrix $\Sigma$ evaluated at $x$ (see Appendix for the derivation of \refeqn{betaik}).

According to the total probability theorem with respect to the association events, the resulting posterior estimate of the state is given by
\begin{align}
\hat x^+_{i_k}=&\hat x^-_{i_k}+\beta_{i_k}K_{i_k}e_{i_k}\label{KalEst},
\end{align}
where the estimator gain is equal to the Kalman gain, i.e., $K_i = P_{i_k}^{-} H_{i_k^T} S_{i_k}^{-1}$, as there is no measurement origination uncertainty when conditioned on the event $\Theta_i$.

@@

The joint probabilistic data association filter described in the previous section is effective in handling clutter or missed detection of multiple targets. However, it is prone to coalesce estimates, especially in targets in close-proximity. Here, we present a coalescence-avoiding optimal JPDAF, hereafter C-JPDAF for short, to avoid data coalescence. The main idea is choosing the estimator gain such that a weighted sum of the size of uncertainty and a measure of similarity is minimized.

@@

The initial estimate of the states are designed to occur shortly before the two trajectories cross paths near $r_{ref}=7000km$ from the center of the earth; for the time to complete a circular orbit at this radius, $t_{ref}=2\pi \sqrt{\frac{r_{ref}^3}{\mu}}$, we can solve for a reference circular orbit $X_{ref}=\begin{bmatrix} r_{ref} & 0 & 0 & \frac{2\pi}{t_{ref}}\end{bmatrix}^T$, then perturb this orbit slightly by $X_{pert}=\begin{bmatrix} 0.40 & 0 & 0 & -1.5\times10^{-5}\end{bmatrix}^T$. We can easily choose the initial conditions to be $X_{1_0}= X_{ref}+X_{pert}$ and $X_{2_0}= X_{ref}-X_{pert}$. The initial estimates are assumed to be relatively accurate: there is no need to simulate large uncertainty when the paths are initially sufficiently far apart because this paper is concerned with the coalescence when the targets are close together, so the state and covariance will have been determined by simulated measurements while the estimates were still spread significantly apart.

\EditTL{Put the values of $P_0$, $Q$ and $R$ here. Describe how the measurements are switched between two satellites. }

Three filtering approaches are applied, namely extended Kalman filter (EKF), JPDAF, and C-JPDAF. For EKF, it is assumed that the correct measurement origination is know with certainty, i.e., all of the measurements are associated to correct target. This serves as an ideal reference case to be compared with JPDAF and C-JPDAF. For the C-JPDAF, the weighting parameters of the cost are chosen as $a=0.02$ and $c=5\times10^{-5}$. We propagate the nonlinear equations of motion numerically using Matlab, and we generate measurement at every $0.1$ seconds with an equal likelihood that its origination is from either target.

@@

\begin{table}
\caption{Estimation results}\label{tab:RMS}
\centerline{
\begin{tabular}{ccc}\hline
Method & RMS Error & Computation time \\\hline
EKF & &\\
JPDAF & &\\
C-JPDAF & & \\\hline
\end{tabular}}
\end{table}

@@

\subsection{Proofs}

\paragraph{Derivation of the Association Probability}

We incorporate all of the assumptions from Section \ref{DAP} to simplify the weighting term for the estimates.
 we consider time step $k$ (subscripts omitted here) that the during the \emph{single} event $\Theta_i$ target $i$ is measured out of $m_k=1$ total measurements inside arbitrary volume $V$.
Because all targets fall inside $V$, the measurement association indicator $\tau=1$ while the number of unassociated measurements $\phi(\Theta_i)=0$; at least one measurement is associated, so the binary target detection indicator $\delta_t(\Theta_i)=1$.
We also consider equal likelihood of detection $P_D$ for each measurement; we generalize the number of estimates to $y$ such that $P_D=\frac{1}{y}$.
From~\cite[Section ?.?]{TrackDataAssoc}, we determine the weighting to be
\begin{align}
\beta_i\equiv P(\Theta_i|z)=&\frac{1}{c}\frac{\phi!}{V}\displaystyle\prod_{j=1}^{m_k} f_{i_j}^{\tau_j}\displaystyle\prod_{i=1}^{2} (P_{D_i})^{\delta_t}(1-P_{D_i})^{1-\delta_t}\\
=&\frac{1}{cV}f_{i}
\end{align}
for normalizing constant $c$ and Gaussian pdf $f_{i}$. Hence, $c$ is defined as
\begin{align}
c=&\frac{1}{V}\displaystyle\sum\limits_{l=1}^y f_{l}.
\end{align}
Therefore, we solve for the simplified weighting
\begin{align}
\beta_i=\frac{f_i}{\displaystyle\sum\limits_{l=1}^y f_{l}}
\end{align}
which is much simpler after assumptions.

\paragraph{Derivation of Posteriori Covariance}

The second proof shows how the measurement updates may take a more manipulatable form under the assumptions. From~\cite{TrackDataAssoc},
\begin{align}
\bar e=&\displaystyle\sum\limits_{i=1}^{m_k}\beta_ie_i=\beta_ie_i\\
\hat x^+_i=&\hat x^-_i+K_i\bar e=\hat x^-_i+\beta_iK_ie_i.
\end{align}
Because only 1 innovation is calculated per target, there is no spread in the innovations term on each target, which is included in the JDPAF without these assumptions. Furthermore we define $\beta_{0_i}$ as the probability that target $i$ is not measured; with only one measurement considered each time step, $\beta_{0_i}=1-\beta_i$. Again from~\cite{TrackDataAssoc},
\begin{align}
P^+_i=&\beta_{0_i}P^-_i+(1-\beta_{0_i})(P^-_i-K_iS_iK_i^T)\\
P^+_i=&(1-\beta_i+\beta_i)P^-_i-\beta_iK_iS_iK_i^T\\
P^+_i=&P^-_i-\beta_iK_iS_iK_i^T
\end{align}

@@

\bibliography{BibMaster}
\bibliographystyle{IEEEtran}

\end{document}
